Contextual Identity: Freedom to be all Your Selves

### 2013-03-06 paper.tex
Change title, clarify incentives to make linking easy

\title{Contextual Identity: Towards Usable Privacy}

@@

Lesbian, gay, bisexual, and transgendered youth are at risk for contextual
identity violations.  Access to support is crucial for LGTB-identified youth,
who are at higher risk for bullying and suicide~\cite{hrc}, though
much of that support is only accessible through the Internet in socially
conservative areas. In 2011 Bobbi Duncan and Taylor McCormick, two
students at the University of Texas at Austin, were inadvertantly outed when
their choir director added them to a Facebook group for Queer
Chorus~\cite{fowler}. Even though both students had blocked their parents from
seeing any personal posts revealing their sexuality, Queer Chorus is a
public group and so Facebook published notifications to Duncan's and McCormick's
friends, including their parents. Duncan later attempted suicide~\cite{duncan}.

@@

\paragraph{Private browsing mode}
Private browsing mode exists in all major browsers, but has no standard
behavior~\cite{ABBJ10}.
Interaction with extensions, treatment of cookies, history, and
bookmarks upon entering and exiting are different across browsers.
Similar to multiple profiles, private browsing mode is not generally secure
against all local attacks.

@@

Service providers are highly incentivized to make linking identities easy;
users need more tools to help separate and curate identities. Without
knowing more about how people think about identity, we concentrate solely on
automating manual processes that users already perform.

>>>>

\title{Contextual Identity: Freedom to be all Your Selves}
%\title{Contextual Identity: All your selves are belong to you}

@@

Lesbian, gay, bisexual, and transgendered youth are at risk for contextual
identity violations.  Access to support is crucial for LGTB-identified youth,
who are at higher risk for bullying and suicide~\cite{hrc}, and
much of that support is only accessible through the Internet in socially
conservative areas. In 2011 Bobbi Duncan and Taylor McCormick, two
students at the University of Texas at Austin, were inadvertantly outed when
their choir director added them to a Facebook group for Queer
Chorus~\cite{fowler}. Even though both students had blocked their parents from
seeing any personal posts revealing their sexuality, Queer Chorus is a
public group and so Facebook published notifications to Duncan's and McCormick's
friends, including their parents. Duncan later attempted suicide~\cite{duncan}.

@@

\paragraph{Private browsing mode}
Private browsing mode exists in all major browsers, but has no standard
behavior~\cite{ABBJ10}.
Interaction with extensions, treatment of cookies, history, and
bookmarks upon entering and exiting are different across browsers.
Similar to multiple profiles, private browsing mode is not secure
against all local attacks.

@@

Service providers compete for customers by providing a platform that
meets all of their needs.  The multiplicity of social media means that
in order to be competitive, social networks encourage cross-linking,
resharing, and resyndication --- all of which promote linking identities.
Linking identities is already easy;
users need more tools to help separate and curate identities. Without
knowing more about how people think about identity, we concentrate solely on
automating manual processes that users already perform.
